---
title: "103-100-inds"
output: html_document
date: "2023-09-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

```{r}
stats<-read_csv("outputs/102/alignment-info.txt", col_names=c("Sample","Reads","Coverage"))
sub<-filter(stats, Reads > (325*200))
```


```{r,eval=FALSE}
test<-sub %>% slice_sample(n=100)
write_tsv(test, file="meta/test100.csv")
```


Now we need commands like this

`../scripts/GTseq_Genotyper_v3_Tetra.pl ../genotyper_input.csv i001_10_4_18225.fastq > i001_10_4_18225.genos`

or in my case 
`./data-processing-files/GTseq_Genotyper_v3_Tetra.pl 103.1-genotyper-in.csv data/align/5D58_3_S160_L002_R1_001.fastq > outputs/102/5D58_3_S160.genos`

```{r}
test<-read_tsv("meta/test100.csv")
test<-test %>% mutate(Fastq=paste0("data/align/",Sample,"_L002_R1_001.fastq")) %>%
  mutate(Command=paste0("perl ./data-processing-files/GTseq_Genotyper_v3_Tetra.pl", " 103.1-genotyper-in.csv ",
         Fastq, " > ", "outputs/103/",Sample,".genos")) %>%
   mutate(Command2=paste0("perl ./data-processing-files/GTseq_Genotyper_v3_Tetra.pl", " data-processing-files/genotyper_input.csv ",
         Fastq, " > ", "outputs/103/",Sample,".org"))
test
```


cpan String::Approx
Installed in 
Installing /home/maccamp/perl5/lib/perl5/x86_64-linux-thread-multi/auto/String/Approx/Approx.so
Installing /home/maccamp/perl5/lib/perl5/x86_64-linux-thread-multi/String/Approx.pm
Installing /home/maccamp/perl5/man/man3/String::Approx.3

For me, I have perl installed with conda, so also maybe

conda install -c bioconda perl-string-approx


But, skipping the interpreter (/usr/bin/perl) works


perl ./data-processing-files/GTseq_Genotyper_v3_Tetra.pl 103.1-genotyper-in.csv data/align/5D58_3_S160_L002_R1_001.fastq > outputs/103/5D58_3_S160.genos


(base) maccamp@farm:~/kootenai$ cat outputs/103/5D58_3_S160.genos
data/align/5D58_3_S160_L002_R1_001.fastq,Raw-Reads:141406,On-Target reads:1634,%On-Target:1.2,IFI_score:9.24
Atr_30916-30,T=160,C=28,5.714,0000,NA,0,0,188,97.9,11.506,Pass,3
Atr_30916-62,G=0,A=0,1.000,0000,NA,0,0,0,0.0,0.000,Pass,0
Atr_39023-30,G=171,A=10,17.100,0000,NA,0,0,181,93.8,11.077,Pass,9
Atr_39023-56,C=0,T=0,1.000,0000,NA,0,0,0,0.0,0.000,Pass,0
Atr_39071-37,G=108,A=26,4.154,GGGA,HET1,0,0,134,93.7,8.201,Pass,5
Atr_39071-73,G=0,A=0,1.000,0000,NA,0,0,0,0.0,0.000,Pass,0
Atr_45890-42,A=75,C=95,0.789,AACC,HET2,1.6,0,284,35.1,17.381,Pass,53
Atr_45890-59,G=0,T=0,1.000,0000,NA,1.6,0,0,0.0,0.000,Pass,0
Atr_46229-48,G=59,A=182,0.324,GAAA,HET3,0,0,241,97.2,14.749,Pass,3
Atr_46229-66,G=0,A=0,1.000,0000,NA,0,0,0,0.0,0.000,Pass,0
Atr_54038-28,A=91,G=1,91.000,AAAA,A1HOM,0,0,92,52.0,5.630,Pass,16
Atr_54038-48,A=0,G=0,1.000,0000,NA,0,0,0,0.0,0.000,Pass,0
Atr_75140-52,C=61,T=22,2.773,CCCT,HET1,0,0,83,100.0,5.080,Pass,0
Atr_75140-58,C=0,T=0,1.000,0000,NA,0,0,0,0.0,0.000,Pass,0
Atr_76571-21,C=104,A=327,0.318,CAAA,HET3,0,0,431,72.0,26.377,Pass,6
Atr_76571-26,C=0,A=0,1.000,0000,NA,0,0,0,0.0,0.000,Pass,0

Seems to work!

But the calls, I had are:
(base) maccamp@farm:~/kootenai/data/GT_Seq/AFST01/genotypes$ grep Atr_30916-62 5D58_3_S160_L002_R1_001.genos 
Atr_30916-62,G=182,A=0,1820.000,GGGG,A1HOM,0,0,182,94.8,0.386,Pass,9

From Peter     
Atr_30916-62,G,A,GACTGGGGCTATTT,GACTGGGACTATTT,AGGTCGTGCTGTATTGGTCA,0,0
Atr_30916-62,G,A,GACTGGGGCTATTT,GACTGGGACTATTT,AGGTCGTGCTGTATTGGTCA,0,0

k, that looks identical.  Maybe we can't resample reads? running two different commands to get genos



Let's get all the inds.

```{r}
test %>% select(Command) %>% write_tsv("103.2-commands.sh", col_names = FALSE)
test %>% select(Command2) %>% write_tsv("103.3-org-commands.sh", col_names = FALSE)

```

module load parallel    
(base) maccamp@farm:~/kootenai$ 
srun -p high -t 1:00:00 --nodes=1 --mem=32GB parallel -j 12 < 103.2-commands.sh     
srun -p high -t 1:00:00 --nodes=1 --mem=32GB parallel -j 10 < 103.3-org-commands.sh     

 for f in *.genos; do echo $f; cat $f | tail -n +2 >> 100-combined.csv; done;
 for f in *.org; do echo $f; cat $f | tail -n +2 >> 100-org-combined.csv; done;

```{r}
genos<-read_csv("outputs/103/100-combined.csv",
                col_names=c("Locus","G1","G2","X4","Genotype","Call","X7","X8","X9","X10","X11","X12","X13"))
orgs<-read_csv("outputs/103/100-org-combined.csv",
                col_names=c("Locus","G1","G2","X4","Genotype","Call","X7","X8","X9","X10","X11","X12","X13"))

genos<-bind_rows(genos,orgs)
```

```{r}
loci<-read_tsv("outputs/103/loci.tsv")
```

```{r}
merge<-left_join(genos, loci) %>% filter(State %in% c("Original","Edited"))
merge2<-merge %>% group_by(Locus, State, Call) %>% summarize(Count=n()) %>% mutate(Total=sum(Count))
merge3<-merge2
merge3$Locus<-gsub("-\\d\\d","",merge3$Locus)
```


```{r}
ggplot(merge3) + geom_col(aes(x=Locus, y=Count, fill=Call)) +
  facet_wrap(.~State, ncol=1) +
  theme_bw() +
  theme(axis.text.x=element_text(angle=45, hjust=1, vjust=1)) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="H", na.value = "grey")

ggsave("outputs/103/test-loci-100inds.jpeg")
```


## What are some other loci to consider?
```{r}
candidates<-orgs %>% left_join(loci) %>% group_by(Locus, Genotype, State) %>% summarize(Count=n()) 
c2<-candidates %>% filter(Count>75) %>% filter(!State %in% c("Unmodified","Original")) 

c3 <- candidates %>% filter(Locus %in% c2$Locus) %>% arrange(Locus, -Count)
c3
```

Probably a pattern like this, homozygote with a high proportion of missing is worth looking at (though this one is probably invariant)

Atr_19783-57	CCCC	NA	63	
Atr_19783-57	0000	NA	30	
Atr_19783-57	CCCA	NA	6	
Atr_19783-57	CCAA	NA	1	

This one has a high proportion of missing ata, and is probably invariant.

Atr_28746-28	0000	NA	80	
Atr_28746-28	TAAA	NA	5	
Atr_28746-28	TTAA	NA	5	
Atr_28746-28	TTTA	NA	5	


Atr_10322-43 two snps
Atr_28746-28 (no snps)
Atr_32545-55 (no snps)	
Atr_32551-51 (no snps)
Atr_35415-62 (no snps)
Atr_38278-50 a SNP 24-CA
Atr_38591-73 (mostly AT)
Atr_65843-52 (mostly GT)
Atr_74987-50 (invariant)
Atr_10867-69	(invariant)
Atr_19783 (invariant)

Can make new loci from:

Atr_10322-43 C/T
Atr_38278-50 C/A
Atr_10428-71 A/T
Atr_14862-38 T/C
Atr_15294-66 T/A

## Let's see what their story is

_Atr_10322-43 C/T_

Atr_10322-43,G,A,GCAGCGAAACAAAGA,GCAGCAAAACAAAGA,TGCAGGGGCTATCAGAGACT,0,0.3

Get six bp flanking

TGCAGGGGCTATCAGAGACT                            AAGATACTTGCTACG
TGCAGGGGCTATCAGAGACTTCACCCAGGGTGAACAAGCAGCGAAACAAAGATACTTGCTACGCTGAGCTCCCACACTGATTAGATCGGAAGAGCACACGT
TGCAGGGGCTATCAGAGACTTCACCCAGGGTGAACAAGCAGCGAAACAAAGATACCTGCTACGCTGAGCTCCCACACTGATTAGATCGGAAGAGCACACGT


_Atr_38278-50 C/A_
position 24 is polymorphic

Atr_38278-50,C,A,GTGCATGCAAACTA,GTGCATGAAAACTA,TCCTCCAAACCACAGTGTGC,0,0
TCCTCCAAACCACAGTGTGCATGCAAACTA
TCCTCCAAACCACAGTGTGCATGAAAACTA

This looks to be the same locus, so we'll keep it.

_Atr_10428-71 A/T_

Atr_10428-71,T,A,AGAGAGCTAGCA,AGAGAGCAAGCA,CGCACACACACAAAGAGAGC,0,2

Sites 21, 54 are polymorphic

Target seqs
CGCACACACACAAAGAGAGCTAGCAGCCCTGGCTTCCTGGAGTGTGGAGAGCTCACAGACACTGTGGCTCTGGATCCAGATCGGAAGAGCACACGTCTGAA
CGCACACACACAAAGAGAGCAAGCAGCCCTGGCTTTCTGGAGTGTGGAGAGCTAACAGACACTGTGGCTCTGGATCCAGATCGGAAGAGCACACGTCTGAA

No change here

_Atr_14862-38 T/C_
expect site 27 to be variable (T/C)
Atr_14862-38,T,C,TTGACTCCCTTTAAG,TTGACCCCCTTTAAG,CGCCTCCCCAGGACTATTTT,0,0

Should work no change made

CGCCTCCCCAGGACTATTTTATTGACTCCCTTTAAGAAATACAATAAAAATGGCCACAGGAAAAGATCGGAAGAGCACACGTCTGAACTCCAGTCACGGCT
CGCCTCCCCAGGACTATTTTATTGACCCCCTTTAAGAAATACAATAAAAATGGCCATAGGAAAAGANCGGAAGAGCACACGTCTGAACTCCAGTCACGNCT

_Atr_15294-66 T/A_



