---
title: "203-multiple snps"
output: html_document
date: "2023-10-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```


Some loci may have variable sites leading to mismatches. 

Looking for highly polymorphic loci....

   3 Atr_11864-68,T,C,ATATCGCTGACCAC,ATATCGCCGACCAC,GGTACCACCGCCAATATCGC,0,0
   3 Atr_13476-65,A,T,TTATCAGTATGCAGC,TTATCTGTATGCAGC,CGTTTTCCAGCACCACAGGT,0.3,0
   3 Atr_18334-74,A,G,ATGGTGGAC,ATGGTGGGC,GGAAGTTGGTCCTCAGAGGC,0,0
   3 Atr_29086-33,C,T,TTGTCAACGGGTTT,TTGTCAATGGGTTT,GGTTTGGTTCAACCGCACAG,0,0
   3 Atr_29414-61,C,T,TTCCAACCGGGGAT,TTCCAACTGGGGAT,CAGGGCTGGGGTCTGGA,0,0
   3 Atr_39071-73,G,A,CTTCACAGAC,CTTCACAAAA,ATAGCCCAGGTGGATGCATG,0,0 # already done
   3 Atr_4677-47,C,G,TCCCGGACCGGGCC,TCCCGGAGCGGGCC,CCTGACACTGGCACTCAACA,0,0 #already done
   3 Atr_48754-60,G,A,CTGCAACGACGTGT,CTGCAACAACGTGT,GCTTTCTCCTTTCAGTGGCC,0,0
   3 Atr_525-66,G,C,AACAAGAAGCAAAGA,AACAACAAGCAAAGA,TCCAGCATGACCATCTCTGC,0,0
   3 Atr_61171-66,C,T,GATGTGACTGCACG,GATGTGATTGCACG,CCGACGCTGTAAGTTCTGGA,0,0
   3 Atr_69217-58,A,G,TCAAAGCACCCGAG,TCAAAGCGCCCGAG,AAGCCCCCTTTCTGCTTCTC,0,0
   3 Atr_7793-68,C,A,CGGTACTCAAATAA,CGGTACTAAAATAA,TAGGGAAAGGGAGTCAGCCA,0,0
   3 Atr_9723-56,C,T,ATGCGCAGTCTGTAG,ATGCGTAGTCTGTAG,TGATGGGCCATCTTTCACGG,0,0
   4 Atr_44473-38,T,C,ACATTGATATCTCA,ACATTGACATCTCA,GCAGGTGGTGGAGCTCATAG,0,2
   4 Atr_49388-52,G,A,CATGTGTGTCTGTC,CATGTGTATCTGTC,GGGACCCATGTATAAGATGGCC,0,0
   4 Atr_5019-45,C,T,TCCTGCAGC[TA]TTCCT,TCCTGTAGC[TA]TTCCT,GCACCGCTGAATGCTACATC,0,0.3
   4 Atr_51999-44,A,G,AATATAATGGGTAAG,AATATGATGGGTAAG,TAGGGTCCCAGGGCAGTTTA,0,0
   4 Atr_54160-70,T,C,TCATTTTTGGGTC,TCATTTTCGGGTC,TTTGCGGTTCAGATGTGGGT,0,0
   4 Atr_59842-43,G,A,GGCGGTTGAACCAG,GGCGGTTAAACCAG,CATCTCTCTTGTGAGGGCGG,0,1.2
   4 Atr_64006-52,C,T,GGTTTACCCTGAAG,GGTTTACTCTGAAG,CTGGATGGGGAGCGGTTTAC,0,0
   4 Atr_64706-45,T,A,CACTGACTGCTGTA,CACTGACAGCTGTA,TGCAGGGATGGTCCTTGTTG,1.9,0
   4 Atr_70167-40,C,T,CAGACCTCGTCCTG,CAGACCTTGTCCTG,GCATGCATCAGATAGCCAGC,0,0
   4 Atr_70479-48,T,A,CATAGATTGCTTCA,CATAGATAGCTTCA,GTCTGGGAAATGTCTGGGCA,1.8,0
   5 Atr_13917-71,C,A,AACTACTCATCA,AACTACTAATCA,CCTTCCCAGGGAGCTTGATG,0,0
   5 Atr_24146-56,A,C,ACATGTTAATCTTG,ACATGTTCATCTTG,TGGCTAAAGATCTAGAACACATGT,0,0
   5 Atr_28411-65,A,G,GTGCCCAACAGGAC,GTGCCCAGCAGGAC,AAACCAAGCAGCGTCTGGAA,0,0
   5 Atr_29277-35,C,G,TGAAACAGCAGTATG,TGAAAGAGCAGTATG,GGATCGCTCTCTGCTTGTGA,0,0
   5 Atr_45890-59,G,T,GTGAGGAGACCTGT,GTGAGGATACCTGT,TAAGGGCTGCAGTGGTGAAG,1.6,0
   7 Atr_16803-66,C,T,GGCAGCACGCCTCT,GGCAGCATGCCTCT,CATGTTGTGTGTCCGGTGC,0,0
   7 Atr_57542-29,A,T,CCAGAAAATGGCTC,CCAGAAATTGGCTC,CTGGCCTTTGTCCTCCAGAA,0,0
   9 Atr_40110-57,G,A,TAGGGCCGCATGCA,TAGGGCCACATGCA,GCACTGTGCCACTGACATAT,0,0
   
Wow, so what happened with these guys?

```{sh, eval=FALSE}
gunzip -c ../200/snps-90-broodstock.geno.gz  | cut -f 1,2 > sites.txt
```

```{r}
polys<-read_tsv("outputs/203/sites.txt", col_names = c("Locus","Site")) %>% group_by(Locus) %>%
  mutate(SNPS=n())
polys  %>% select(Locus, SNPS) %>% unique() %>% arrange(-SNPS)
```


```{r}
pl<-polys  %>% select(Locus, SNPS) %>% unique() %>% arrange(-SNPS) %>% filter(SNPS>=4) %>% separate(Locus, sep=",", into = c("Loci","G1","G2","R1","R2","Primer","X1","X2"))
pl
```


Get genos

```{r}
load("outputs/201/reads.rda")
```

```{r}
combo<-reads %>% left_join(parents %>% select(Sample, Type), by=c("Sample"="Sample")) 
combo %>% select(Sample, Type) %>% unique() %>% group_by(Type) %>% summarize(Count=n())
```

```{r}
combo %>% filter(Locus %in% pl$Loci) %>% group_by(Locus, Genotype, Call) %>% summarize(Count=n())
```

```{r}
combo %>% filter(Locus %in% pl$Loci) %>% group_by(Locus, Genotype, Call) %>% summarize(Count=n()) %>%
  filter(Call=="A2HOM") %>% arrange(-Count)
```

```{r}
combo %>% filter(Locus %in% pl$Loci) %>% group_by(Locus, Genotype, Call) %>% summarize(Count=n()) %>% filter(Locus=="Atr_54160-70")
```

    
_1_  
   4 Atr_70479-48,T,A,CATAGATTGCTTCA,CATAGATAGCTTCA,GTCTGGGAAATGTCTGGGCA,1.8,0
   
(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCTGGGAAATGTCTGGGCA test.fastq --color | grep CATAGATTGCTTCA | wc
   3317    3317  338334
(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCTGGGAAATGTCTGGGCA test.fastq --color | grep CATAGATAGCTTCA | wc
     46      46    4692


Has a lot of missing data, other sites a lot more variable: not to self compute MAFs from vcf.
Could try something like this:
Atr_70479-52,G,A,TGGTCAGATGCCT,TGGTCAAATGCCT,GTCTGGGAAATGTCTGGGCA,1.8,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCTGGGAAATGTCTGGGCA test.fastq  --color | grep TGGTCAGATGCCT | wc
   1417    1417  144534
(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCTGGGAAATGTCTGGGCA test.fastq  --color | grep TGGTCAAATGCCT | wc
   1959    1959  199818

_2_    4 Atr_70167-40,C,T,CAGACCTCGTCCTG,CAGACCTTGTCCTG,GCATGCATCAGATAGCCAGC,0,0

Mostly NA and A2 HOMS, 12/19 look nicely variable, looks like this is off target amplification. Sigh. not worth messing with. This leads to low counts.
(base) maccamp@farm:~/kootenai/outputs/201$ cat test.fastq | grep GCATGCATCAGATAGCCA --color  | grep CAGACCTCGTCCTG | wc
     86      86    8772
(base) maccamp@farm:~/kootenai/outputs/201$ cat test.fastq | grep GCATGCATCAGATAGCCA --color  | grep CAGACCTTGTCCTG | wc
    190     190   19380

Could do something like this:
Atr_00001-40,G,C,AGCCAGCAGCAC,AGCCACCAGCAC,GCATGCATCAGATAGCCAGC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ cat test.fastq | grep GCATGCATCAGATAGCCA --color   | grep AGCCAGCAGCAC | wc
   1915    1915  195330
(base) maccamp@farm:~/kootenai/outputs/201$ cat test.fastq | grep GCATGCATCAGATAGCCA --color   | grep AGCCACCAGCAC | wc
    119     119   12138

_3_    4 Atr_64706-45,T,A,CACTGACTGCTGTA,CACTGACAGCTGTA,TGCAGGGATGGTCCTTGTTG,1.9,0 (this one should work great, skipping)


_4_ Atr_28411-65 looks to be mostly A1 Hom
   5 Atr_28411-65,A,G,GTGCCCAACAGGAC,GTGCCCAGCAGGAC,AAACCAAGCAGCGTCTGGAA,0,0
   
(base) maccamp@farm:~/kootenai/outputs/201$ grep AAACCAAGCAGCGTCTGGAA test.fastq  --color | grep GTGCCCAACAGGAC | wc
   1538    1538  156876
(base) maccamp@farm:~/kootenai/outputs/201$ grep AAACCAAGCAGCGTCTGGAA test.fastq  --color | grep GTGCCCAGCAGGAC | wc
      7       7     714

There are definitely some variable sites screwing with this one, moving to site 58
Atr_28411-65,T,C,ATGAGTTCCTG,ATGAGTCCCTG,AAACCAAGCAGCGTCTGGAA,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep AAACCAAGCAGCGTCTGGAA test.fastq  --color | grep ATGAGTTCCTG | wc
   1544    1544  157488
(base) maccamp@farm:~/kootenai/outputs/201$ grep AAACCAAGCAGCGTCTGGAA test.fastq  --color | grep ATGAGTCCCTG | wc
   1683    1683  171666
   
_5_
Atr_13917-71

   5 Atr_13917-71,C,A,AACTACTCATCA,AACTACTAATCA,CCTTCCCAGGGAGCTTGATG,0,0

Need to adjust for mutation here in regex,
                 
Atr_13917-47,G,C,TTTTGTCTGAA,TTTTCTCTGAA,CCTTCCCAGGGAGCTTGATG,0,0

_6_    4 Atr_59842-43,G,A,GGCGGTTGAACCAG,GGCGGTTAAACCAG,CATCTCTCTTGTGAGGGCGG,0,1.2

(base) maccamp@farm:~/kootenai/outputs/201$ grep CATCTCTCTTGTGAGGGCGG test.fastq | grep GGCGGTTGAACCAG | wc
   1172    1172  119544
(base) maccamp@farm:~/kootenai/outputs/201$ grep CATCTCTCTTGTGAGGGCGG test.fastq | grep GGCGGTTAAACCAG | wc
    798     798   81396
    

This site (23) should work well , NA may be low copy number.

_6_ Atr_64706
                      CACTGACAGCTGTA
   4 Atr_64706-45,T,A,CACTGACTGCTGTA,CACTGACAGCTGTA,TGCAGGGATGGTCCTTGTTG,1.9,0
This site should work well , NA may be low copy number.

_7_ Atr_44473-38	
   4 Atr_44473-38,T,C,ACATTGATATCTCA,ACATTGACATCTCA,GCAGGTGGTGGAGCTCATAG,0,2
(base) maccamp@farm:~/kootenai/outputs/201$ grep GCAGGTGGTGGAGCTCATAG test.fastq | grep ACATTGATATCTCA | wc
   1208    1208  123216
(base) maccamp@farm:~/kootenai/outputs/201$ grep GCAGGTGGTGGAGCTCATAG test.fastq | grep ACATTGACATCTCA | wc
   1190    1190  121380

Should work well.

_8_    5 Atr_45890-59,G,T,GTGAGGAGACCTGT,GTGAGGATACCTGT,TAAGGGCTGCAGTGGTGAAG,1.6,0
Don't expect GT polymorphism her, is CA, also AG poly in binding site
(base) maccamp@farm:~/kootenai/outputs/201$ grep TAAGGGCTGCAGTGGTGAAG test.fastq  --color | grep GTGAGGAGACCTGT | wc
   1547    1547  157794
(base) maccamp@farm:~/kootenai/outputs/201$ grep TAAGGGCTGCAGTGGTGAAG test.fastq  --color | grep GTGAGGATACCTGT | wc
      0       0       0
(

Atr_45890-42,A,C,GAGGAGACCTGTCT,GAGGAGCCCTGTCT,TAAGGGCTGCAGTGGTGAAG,1.6,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep TAAGGGCTGCAGTGGTGAAG test.fastq  --color | grep GAGGAGACCTGTCT | wc
   1544    1544  157488
(base) maccamp@farm:~/kootenai/outputs/201$ grep TAAGGGCTGCAGTGGTGAAG test.fastq  --color | grep GAGGAGCCCTGTCT | wc
    872     872   88944

_9_    4 Atr_64006-52,C,T,GGTTTACCCTGAAG,GGTTTACTCTGAAG,CTGGATGGGGAGCGGTTTAC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color CTGGATGGGGAGC test.fastq  | grep GGTTTACCCTGAAG | wc
   1480    1480  150960
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color CTGGATGGGGAGC test.fastq  | grep GGTTTACTCTGAAG | wc
      5       5     510

Site 14 looks to be a better one to redesign on, GA

Atr_64006-14,G,A,AGCGGTTTACA,AGCAGTTTACA,CTGGATGGGGAGCGGTTTAC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color CTGGATGGGGAGC test.fastq  | grep  AGCGGTTTACA | wc
   4413    4413  450126
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color CTGGATGGGGAGC test.fastq  | grep  AGCAGTTTACA | wc
    157     157   16014

_10_    4 Atr_49388-52,G,A,CATGTGTGTCTGTC,CATGTGTATCTGTC,GGGACCCATGTATAAGATGGCC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGGACCCATGTATAAGATGGCC test.fastq  | grep CATGTGTGTCTGTC | wc -l
1282
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGGACCCATGTATAAGATGGCC test.fastq  | grep CATGTGTATCTGTC | wc -l
516

Trying site 47
Atr_49388-47,T,G,ATACCGTGTGAAC,ATACCGGGTGAAC,GGGACCCATGTATAAGATGGCC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGGACCCATGTATAAGATGGCC test.fastq  | grep ATACCGTGTGAAC | wc
   1797    1797  183294
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGGACCCATGTATAAGATGGCC test.fastq  | grep ATACCGGGTGAAC | wc
    638     638   65076
    
_11_ Atr_51999-44,A,G,AATATAATGGGTAAG,AATATGATGGGTAAG,TAGGGTCCCAGGGCAGTTTA,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color TAGGGTCCCAGGGCAGTTTA test.fastq | grep AATATAATGGGTAAG | wc
    494     494   50388
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color TAGGGTCCCAGGGCAGTTTA test.fastq | grep AATATGATGGGTAAG | wc
     73      73    7446

Looks to be TA polymorphic    sites 34/35 both poly
Atr_51999-34,A,G,GAATATAATGGGTA,GAATATGATGGGTAA,TAGGGTCCCAGGGCAGTTTA,0,0, no real improvement here

_12_     5 Atr_29277-35,C,G,TGAAACAGCAGTATG,TGAAAGAGCAGTATG,GGATCGCTCTCTGCTTGTGA,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGATCGCTCTCTGCTTGTGA test.fastq  | grep TGAAACAGCAGTATG | wc
    404     404   41208
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGATCGCTCTCTGCTTGTGA test.fastq  | grep TGAAAGAGCAGTATG | wc
   1084    1084  110568

This regex looks to hit a variable site, adjusting
Atr_29277-31,C,G,ATGAAACAGCAGT,ATGAAAGAGCAGT,GGATCGCTCTCTGCTTGTGA,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGATCGCTCTCTGCTTGTGA test.fastq  | grep ATGAAACAGCAGT | wc
    406     406   41412
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGATCGCTCTCTGCTTGTGA test.fastq  | grep ATGAAAGAGCAGT | wc
   2544    2544  259488
   
_13_    7 Atr_57542-29,A,T,CCAGAAAATGGCTC,CCAGAAATTGGCTC,CTGGCCTTTGTCCTCCAGAA,0,0
(base) maccamp@farm:~/kootenai/outputs/201$ grep CTGGCCTTTGTCCTCCAGAA test.fastq | grep CCAGAAATTGGCTC | wc
   1695    1695  172890

(base) maccamp@farm:~/kootenai/outputs/201$ grep CTGGCCTTTGTCCTCCAGAA test.fastq | grep CCAGAAAATGGCTC | wc
    116     116   11832
Let's see if a linked SNP is ruining everything. Yes indeedy!

(base) maccamp@farm:~/kootenai/outputs/201$ grep CTGGCCTTTGTCCTCCAGAA test.fastq | grep CCAGAAATTGG | wc
   1709    1709  174318
   
(base) maccamp@farm:~/kootenai/outputs/201$ grep CTGGCCTTTGTCCTCCAGAA test.fastq | grep CCAGAATTTGG | wc
   1109    1109  113118

Atr_57542-29,A,T,CCAGAAATTGG,CCAGAATTTGG,GGATCGCTCTCTGCTTGTGA,0,0

_14_    5 Atr_24146-56,A,C,ACATGTTAATCTTG,ACATGTTCATCTTG,TGGCTAAAGATCTAGAACACATGT,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep TGGCTAAAGATCTAGAACACATGT test.fastq | grep ACATGTTAATCTTG | wc
    239     239   24378
(base) maccamp@farm:~/kootenai/outputs/201$ grep TGGCTAAAGATCTAGAACACATGT test.fastq | grep ACATGTTCATCTTG | wc
   2303    2303  234906

Looks like site 26, with polys at 30 and 33, a variant linked to something 

TGGCTAAAGATCTAGAACACATGTTAATCTTGACTAATTAAGACAATACTTGGTTCCATTAAGCAACAGAGCTCGGTTGAAGATCGGAAGAGCACACGTCT
TGGCTAAAGATCTAGAACACATGTTAATCGTGGCTAATTAAGCCAATAATTGGTGCAATTAAGCAACAGAGCTCGGTTGAAGATCGGAAGAGCACACGTCT

(base) maccamp@farm:~/kootenai/outputs/201$ grep TGGCTAAAGATCTAGAACACATGT test.fastq | grep ACATGTTAATC | wc -l
425
(base) maccamp@farm:~/kootenai/outputs/201$ grep TGGCTAAAGATCTAGAACACATGT test.fastq | grep ACATGTTCATC | wc -l
2318

Atr_24146-26,A,C,ACATGTTAATC,ACATGTTCATC,TGGCTAAAGATCTAGAACACATGT,0,0
Atr_24146-56,A,C,ACATGTTAATCTTG,ACATGTTCATCTTG,TGGCTAAAGATCTAGAACACATGT,0,0

_15_    7 Atr_16803-66,C,T,GGCAGCACGCCTCT,GGCAGCATGCCTCT,CATGTTGTGTGTCCGGTGC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep CATGTTGTGTGTCCGGTGC test.fastq  | grep GGCAGCACGCCTCT --color | wc
   1082    1082  110364
(base) maccamp@farm:~/kootenai/outputs/201$ grep CATGTTGTGTGTCCGGTGC test.fastq  | grep GGCAGCATGCCTCT --color | wc
    555     555   56610

GGCAGCAC[A|G]

GGCAGCACG
Also some indel poly, skipping!

_16_ Atr_54160-70,T,C,TCATTTTTGGGTC,TCATTTTCGGGTC,TTTGCGGTTCAGATGTGGGT,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep TTTGCGGTTCAGATGTGGGT test.fastq | wc
  16851   16851 1718802
(base) maccamp@farm:~/kootenai/outputs/201$ grep TTTGCGGTTCAGATGTGGGT test.fastq | grep TCATTTTTGGGTC | wc
    887     887   90474
(base) maccamp@farm:~/kootenai/outputs/201$ grep TTTGCGGTTCAGATGTGGGT test.fastq | grep TCATTTTCGGGTC  | wc
    765     765   78030

Hmmm.... Some cross amplification, but should work ok.

_17_   4 Atr_5019-45,C,T,TCCTGCAGC[TA]TTCCT,TCCTGTAGC[TA]TTCCT,GCACCGCTGAATGCTACATC,0,0.3

Trying site 31 as an alternative
Atr_5019-31,A,G,TTTCAAATCCTG,TTTCAAGTCCTG,GCACCGCTGAATGCTACATC,0,0.3

(base) maccamp@farm:~/kootenai/outputs/201$ grep GCACCGCTGAATGCTACATC test.fastq | grep TTTCAAATCCTG  | wc
   1072    1072  109344
(base) maccamp@farm:~/kootenai/outputs/201$ grep GCACCGCTGAATGCTACATC test.fastq | grep TTTCAAGTCCTG | wc
    480     480   48960

_18_ Atr_9723-56

   3 Atr_9723-56,C,T,ATGCGCAGTCTGTAG,ATGCGTAGTCTGTAG,TGATGGGCCATCTTTCACGG,0,0
   
Hmm, looks to be some variation around the sites 30,32,35, with 35 being the one targetted originally   

(base) maccamp@farm:~/kootenai/outputs/201$ grep ^TGATGGGCCATCTTTCACGG test.fastq | grep ATGCGCAGTCTGTAG | wc
    796     796   81192
(base) maccamp@farm:~/kootenai/outputs/201$ grep ^TGATGGGCCATCTTTCACGG test.fastq | grep ATGCGTAGTCTGTAG | wc
    252     252   25704
Atr_9723-35,C,T,CGCAGTCTGTAGGGT,CGTAGTCTGTAGGGT,TGATGGGCCATCTTTCACGG,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep ^TGATGGGCCATCTTTCACGG test.fastq | grep CGCAGTCTGTAGGGT | wc
    802     802   81804

(base) maccamp@farm:~/kootenai/outputs/201$ grep ^TGATGGGCCATCTTTCACGG test.fastq | grep CGTAGTCTGTAGGGT | wc
   1250    1250  127500

Hooray!!!

_19_    3 Atr_7793-68,C,A,CGGTACTCAAATAA,CGGTACTAAAATAA,TAGGGAAAGGGAGTCAGCCA,0,0

Sites 35, 46 and 62
grep ^TAGGGAAAGGGAGTCAGCCA test.fastq  | grep CGGTACTCAAATAA | wc
    734     734   74868
    
 grep ^TAGGGAAAGGGAGTCAGCCA test.fastq  | grep CGGTACTAAAATAA | wc
0 

Poly in binding site linked to other SNP, snp not vairable in these fish.
Atr_7793-35,A,G,AGAGTGCAGTAC,AGAGTGCGGTAC,TAGGGAAAGGGAGTCAGCCA,0,0
(base) maccamp@farm:~/kootenai/outputs/201$ grep ^TAGGGAAAGGGAGTCAGCCA test.fastq  | grep AGAGTGCAGTAC | wc
    531
(base) maccamp@farm:~/kootenai/outputs/201$ grep ^TAGGGAAAGGGAGTCAGCCA test.fastq  | grep AGAGTGCGGTAC | wc
    740     740   75480

_20_    3 Atr_69217-58,A,G,TCAAAGCACCCGAG,TCAAAGCGCCCGAG,AAGCCCCCTTTCTGCTTCTC,0,0


Sites 24, 25 29 poly

(base) maccamp@farm:~/kootenai/outputs/201$ grep AAGCCCCCTTTCTGCTTCTC test.fastq  --color | grep TCAAAGCACCCGAG | wc
     74      74    7548
(base) maccamp@farm:~/kootenai/outputs/201$ grep AAGCCCCCTTTCTGCTTCTC test.fastq  --color | grep TCAAAGCGCCCGAG | wc
    238     238   24276

Atr_69217-29,C,A,CCCGAGTCACT,CCAGAGTCACT,AAGCCCCCTTTCTGCTTCTC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep AAGCCCCCTTTCTGCTTCTC test.fastq  --color | grep CCCGAGTCACT | wc
    311     311   31722
(base) maccamp@farm:~/kootenai/outputs/201$ grep AAGCCCCCTTTCTGCTTCTC test.fastq  --color | grep CCAGAGTCACT | wc
    142     142   14484


_21_ Atr_61171-66,C,T,GATGTGACTGCACG,GATGTGATTGCACG,CCGACGCTGTAAGTTCTGGA,0,0

sites 26 34 58

(base) maccamp@farm:~/kootenai/outputs/201$ grep CCGACGCTGTAAGTTCTGGA test.fastq  --color | grep GATGTGACTGCACG | wc
    682     682   69564
(base) maccamp@farm:~/kootenai/outputs/201$ grep CCGACGCTGTAAGTTCTGGA test.fastq  --color | grep GATGTGATTGCACG | wc
    837     837   85374

should work great
                                         AACAAGAAGCAAAGA  
_22_    3 Atr_525-66,G,C,AACAAGAAGCAAAGA,AACAACAAGCAAAGA,TCCAGCATGACCATCTCTGC,0,0
Sites 41, 51, 52 poly GA GA AC

(base) maccamp@farm:~/kootenai/outputs/201$ grep TCCAGCATGACCATCTCTGC test.fastq | grep AACAAGAAGCAAAGA  | wc
   1474    1474  150348
(base) maccamp@farm:~/kootenai/outputs/201$ grep TCCAGCATGACCATCTCTGC test.fastq | grep AACAACAAGCAAAGA  | wc
    106     106   10812

This site is triallelic, site 51 that is 41 looks a lot easier to deal with.

Atr_525-41,G,A,TGCAGGAGCAAC,TGCAAGAGCAAC,TCCAGCATGACCATCTCTGC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep TCCAGCATGACCATCTCTGC test.fastq | grep TGCAGGAGCAAC | wc
   1569    1569  160038
(base) maccamp@farm:~/kootenai/outputs/201$ grep TCCAGCATGACCATCTCTGC test.fastq | grep TGCAAGAGCAAC | wc
   1313    1313  133926

_23_    3 Atr_48754-60,G,A,CTGCAACGACGTGT,CTGCAACAACGTGT,GCTTTCTCCTTTCAGTGGCC,0,0

Site 14 TA is truly a poly
base) maccamp@farm:~/kootenai/outputs/201$ grep GCTTTCTCCTTTCAGTGGCC test.fastq  | grep CTGCAACGACGTGT | wc
    213     213   21726
(base) maccamp@farm:~/kootenai/outputs/201$ grep GCTTTCTCCTTTCAGTGGCC test.fastq  | grep CTGCAACAACGTGT | wc
      0       0       0

188, 196
Atr_48754-14,T,A,CTGTGGCCTTGTGACA,CAGTGGCCTTGTGACA,GCTTTCTCCTTTCAGTGGCC,0,0

_24_    3 Atr_29414-61,C,T,TTCCAACCGGGGAT,TTCCAACTGGGGAT,CAGGGCTGGGGTCTGGA,0,0

45, 59, 61 look poly

(base) maccamp@farm:~/kootenai/outputs/201$ grep CAGGGCTGGGGTCTGGA test.fastq  | grep TTCCAACCGGGGAT | wc
    922     922   94044
(base) maccamp@farm:~/kootenai/outputs/201$ grep CAGGGCTGGGGTCTGGA test.fastq  | grep TTCCAACTGGGGAT | wc
   1332    1332  135864
This one looks like it should work well. site 61 does mess with things
Atr_29414-59,TGGAGTTCCAACCG,TGGAGTTCCAACTG,CAGGGCTGGGGTCTGGA,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep CAGGGCTGGGGTCTGGA test.fastq  | grep TGGAGTTCCAACCG | wc
   1473    1473  150246
(base) maccamp@farm:~/kootenai/outputs/201$ grep CAGGGCTGGGGTCTGGA test.fastq  | grep TGGAGTTCCAACTG | wc
   1335    1335  136170
   
   
_25_    3 Atr_29086-33,C,T,TTGTCAACGGGTTT,TTGTCAATGGGTTT,GGTTTGGTTCAACCGCACAG,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep GGTTTGGTTCAACCGCACAG test.fastq | grep TTGTCAACGGGTTT | wc
    707     707   72114
(base) maccamp@farm:~/kootenai/outputs/201$ grep GGTTTGGTTCAACCGCACAG test.fastq | grep TTGTCAATGGGTTT | wc
    480     480   48960

This one is hard to clearly improve upon.

_26_    3 Atr_18334-74,A,G,ATGGTGGAC,ATGGTGGGC,GGAAGTTGGTCCTCAGAGGC,0,0
This one is hard to clearly improve upon.

_27_    3 Atr_13476-65,A,T,TTATCAGTATGCAGC,TTATCTGTATGCAGC,CGTTTTCCAGCACCACAGGT,0.3,0

Sites 36, 37 41
(base) maccamp@farm:~/kootenai/outputs/201$ grep CGTTTTCCAGCACCACAGGT test.fastq  | grep TTATCAGTATGCAGC | wc
   1866    1866  190332
(base) maccamp@farm:~/kootenai/outputs/201$ grep CGTTTTCCAGCACCACAGGT test.fastq  | grep TTATCTGTATGCAGC | wc
   1128    1128  115056

Should work pretty well
                                          ATATCGCTGACCAC
_28_    3 Atr_11864-68,T,C,ATATCGCTGACCAC,ATATCGCCGACCAC,GGTACCACCGCCAATATCGC,0,0

21,40,45 

(base) maccamp@farm:~/kootenai/outputs/201$ grep GGTACCACCGCCAATATCGC test.fastq  | grep ATATCGCTGACCAC | wc
   1326    1326  135252
(base) maccamp@farm:~/kootenai/outputs/201$ grep GGTACCACCGCCAATATCGC test.fastq  | grep ATATCGCCGACCAC | wc
    659     659   67218
This is targeting site 21 (TC) should work great!!

These doubles look close to each other
Atr_13706-54,A,T,GTGAGAGAAGACTA,GTGAGAGTAGACTA,AGGCTACTTGCATCTGCCAG,0,0	74
Atr_13706-54,A,T,GTGAGAGAAGACTA,GTGAGAGTAGACTA,AGGCTACTTGCATCTGCCAG,0,0	76
Atr_14635-67,C,A,GGAGCACCAAAAAC,GGAGCACAAAAAAC,ATCCCCAGCTGATTTGCCTC,0,0.3	58
Atr_14635-67,C,A,GGAGCACCAAAAAC,GGAGCACAAAAAAC,ATCCCCAGCTGATTTGCCTC,0,0.3	59
Atr_22727-31,C,T,TTTGCCAGATTTCAG,TTTGCTAGATTTCAG,GCAGGAAACCATGATGCACC,0,0	73
Atr_22727-31,C,T,TTTGCCAGATTTCAG,TTTGCTAGATTTCAG,GCAGGAAACCATGATGCACC,0,0	75
Atr_2768-35,C,T,CGCCTGGCCAGTTG,CGCCTGGTCAGTTG,TGCAGGTGTTCAGTTGAGCA,0,0	30
Atr_2768-35,C,T,CGCCTGGCCAGTTG,CGCCTGGTCAGTTG,TGCAGGTGTTCAGTTGAGCA,0,0	35

Atr_39023-56,C,T,AGTGACACGGAGAG,AGTGACATGGAGAG,GGTCCACCTGTCAATAATGGC,0,0	23
Atr_39023-56,C,T,AGTGACACGGAGAG,AGTGACATGGAGAG,GGTCCACCTGTCAATAATGGC,0,0	30
Atr_43107-50,G,A,ATCTGCTGTAGCAC,ATCTGCTATAGCAC,GGTGTCTGCCTGAGCTCAAT,0,0	70
Atr_43107-50,G,A,ATCTGCTGTAGCAC,ATCTGCTATAGCAC,GGTGTCTGCCTGAGCTCAAT,0,0	72
Atr_46134-46,T,C,TCCCTGCTGATTTT,TCCCTGCCGATTTT,TGCTTGACCTAGCCAGTAGTG,0.3,0	46
Atr_46134-46,T,C,TCCCTGCTGATTTT,TCCCTGCCGATTTT,TGCTTGACCTAGCCAGTAGTG,0.3,0	47
Atr_46247-56,C,T,TAAACCGGGGCTCTG,TAAACTGGGGCTCTG,GTCAGGGACTCGTGGACTTC,0,0	29
Atr_46247-56,C,T,TAAACCGGGGCTCTG,TAAACTGGGGCTCTG,GTCAGGGACTCGTGGACTTC,0,0	30
Atr_59201-47,G,A,CAGCAGGGTCCACT,CAGCAGGATCCACC,GCTTGATTTCACTGGGTGCC,0,0	36
Atr_59201-47,G,A,CAGCAGGGTCCACT,CAGCAGGATCCACC,GCTTGATTTCACTGGGTGCC,0,0	42
Atr_64217-68,A,G,CCTTAAATTCGAG,CCTTAGATTCGAG,TGTTAACAAGGGAAACGCCG,0,0	30
Atr_64217-68,A,G,CCTTAAATTCGAG,CCTTAGATTCGAG,TGTTAACAAGGGAAACGCCG,0,0	38
Atr_68186-72,C,T,ACAGTCCCTGC,ACAGTCCTTGC,TACCAGTCGCCTGACCAGTA,0,0	52
Atr_68186-72,C,T,ACAGTCCCTGC,ACAGTCCTTGC,TACCAGTCGCCTGACCAGTA,0,0	58


_29_                           CGCCTGGCCAGTTG
Atr_2768-35,C,T,CGCCTGGCCAGTTG,CGCCTGGTCAGTTG,TGCAGGTGTTCAGTTGAGCA,0,0	30
Atr_2768-35,C,T,CGCCTGGCCAGTTG,CGCCTGGTCAGTTG,TGCAGGTGTTCAGTTGAGCA,0,0	35

Poly here interferse
(base) maccamp@farm:~/kootenai/outputs/201$ grep TGCAGGTGTTCAGTTGAGCA test.fastq  | grep CGCCTGGCCAGTTG | wc
    216     216   22032
(base) maccamp@farm:~/kootenai/outputs/201$ grep TGCAGGTGTTCAGTTGAGCA test.fastq  | grep CGCCTGGTCAGTTG | wc
    160     160   16320

Atr_2768-34,C,T,CTGGCCAGTTGGG,CTGGTCAGTTGGG,TGCAGGTGTTCAGTTGAGCA,0,0	

(base) maccamp@farm:~/kootenai/outputs/201$ grep TGCAGGTGTTCAGTTGAGCA test.fastq  | grep CTGGCCAGTTGGG | wc
    731     731   74562
(base) maccamp@farm:~/kootenai/outputs/201$ grep TGCAGGTGTTCAGTTGAGCA test.fastq  | grep CTGGTCAGTTGGG | wc
    162     162   16524

_30_ 
Atr_39023-56,C,T,AGTGACACGGAGAG,AGTGACATGGAGAG,GGTCCACCTGTCAATAATGGC,0,0	23
Atr_39023-56,C,T,AGTGACACGGAGAG,AGTGACATGGAGAG,GGTCCACCTGTCAATAATGGC,0,0	30

(base) maccamp@farm:~/kootenai/outputs/201$ grep GGTCCACCTGTCAATAATGGC test.fastq  | grep AGTGACACGGAGAG | wc
   1489    1489  151878
(base) maccamp@farm:~/kootenai/outputs/201$ grep GGTCCACCTGTCAATAATGGC test.fastq  | grep AGTGACATGGAGAG | wc
     55      55    5610

Leaving this alone

_31_
Atr_43107-50,G,A,ATCTGCTGTAGCAC,ATCTGCTATAGCAC,GGTGTCTGCCTGAGCTCAAT,0,0	70
Atr_43107-50,G,A,ATCTGCTGTAGCAC,ATCTGCTATAGCAC,GGTGTCTGCCTGAGCTCAAT,0,0	72

(base) maccamp@farm:~/kootenai/outputs/201$ grep GGTGTCTGCCTGAGCTCAAT test.fastq  | grep ATCTGCTGTAGCAC | wc
    733     733   74766
(base) maccamp@farm:~/kootenai/outputs/201$ grep GGTGTCTGCCTGAGCTCAAT test.fastq  | grep ATCTGCTATAGCAC | wc
      6       6     612

Not a lot to do here!

_32_ 
Atr_46134-46,T,C,TCCCTGCTGATTTT,TCCCTGCCGATTTT,TGCTTGACCTAGCCAGTAGTG,0.3,0	46
Atr_46134-46,T,C,TCCCTGCTGATTTT,TCCCTGCCGATTTT,TGCTTGACCTAGCCAGTAGTG,0.3,0	47

(base) maccamp@farm:~/kootenai/outputs/201$ grep TGCTTGACCTAGCCAGTAGTG test.fastq | grep TCCCTGCTGATTTT | wc
    736     736   75072
(base) maccamp@farm:~/kootenai/outputs/201$ grep TGCTTGACCTAGCCAGTAGTG test.fastq | grep TCCCTGCCGATTTT | wc
     74      74    7548

_33_ Atr_46247-56,C,T,TAAACCGGGGCTCTG,TAAACTGGGGCTCTG,GTCAGGGACTCGTGGACTTC,0,0	29

29/30 both poly
(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCAGGGACTCGTGGACTTC test.fastq  | grep TAAACCGGGGCTCTG | wc
    363     363   37026
(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCAGGGACTCGTGGACTTC test.fastq  | grep TAAACTGGGGCTCTG | wc
    510     510   52020

(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCAGGGACTCGTGGACTTC test.fastq  | grep AAACTGGGGCTCTG | wc
    513     513   52326
(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCAGGGACTCGTGGACTTC test.fastq  | grep AAACCAGGGCTCTG | wc
    313     313   31926

Atr_46247-29,C,T,GGACTTCCTGTAAACT,GGACTTCCTGTAAACCA,GTCAGGGACTCGTGGACTTC,0,0
GGACTTCCTGTAAACT
GGACTTCCTGTAAACCA   

(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCAGGGACTCGTGGACTTC test.fastq  | grep GGACTTCCTGTAAACT | wc
    525     525   53550
(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCAGGGACTCGTGGACTTC test.fastq  | grep GGACTTCCTGTAAACCA | wc
    318     318   32436
    
NOT changing

_34_ 
Atr_59201-47,G,A,CAGCAGGGTCCACT,CAGCAGGATCCACC,GCTTGATTTCACTGGGTGCC,0,0	36
Atr_59201-47,G,A,CAGCAGGGTCCACT,CAGCAGGATCCACC,GCTTGATTTCACTGGGTGCC,0,0	42

Blargh.



## Get laoded 

```{r}
parents<-read_csv("meta/kootenai-all.csv") %>% filter(Type=="broodstock")
parents$Sample<-gsub("/home/maccamp/kootenai/data/align/","",parents$Sample)
parents
```

```{r}
parents %>% 
  mutate(Command2=paste0("perl ./data-processing-files/GTseq_Genotyper_v3_Tetra.pl", 
                         " 203.1-poly-edited ",
         paste0("data/align/",SeqID,"_L002_R1_001.fastq"), " > ", "outputs/203/",Sample,".edited"))%>% 
  select(Command2) %>% write_tsv("203.4-broodstock-commands.sh", col_names = FALSE)

parents %>% 
  mutate(Command2=paste0("perl ./data-processing-files/GTseq_Genotyper_v3_Tetra.pl", 
                         " 203.2-poly-original ",
         paste0("data/align/",SeqID,"_L002_R1_001.fastq"), " > ", "outputs/203/",Sample,".original"))%>% 
  select(Command2) %>% write_tsv("203.5-broodstock-commands.sh", col_names = FALSE)
```

module load parallel    
srun -p high -t 2:00:00 --nodes=1 --mem=32GB parallel -j 12 < 201.4-broodstock-commands.sh     
srun -p high -t 2:00:00 --nodes=1 --mem=32GB parallel -j 12 < 201.5-broodstock-commands.sh     

for f in *.edited; do echo $f; cat $f | tail -n +2 >> 201-combined.csv; done;
for f in *.original; do echo $f; cat $f | tail -n +2 >> 201-org-combined.csv; done;
