---
title: "203-multiple snps"
output: html_document
date: "2023-10-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```


Some loci may have variable sites leading to mismatches. 

Looking for highly polymorphic loci....

   3 Atr_11864-68,T,C,ATATCGCTGACCAC,ATATCGCCGACCAC,GGTACCACCGCCAATATCGC,0,0
   3 Atr_13476-65,A,T,TTATCAGTATGCAGC,TTATCTGTATGCAGC,CGTTTTCCAGCACCACAGGT,0.3,0
   3 Atr_18334-74,A,G,ATGGTGGAC,ATGGTGGGC,GGAAGTTGGTCCTCAGAGGC,0,0
   3 Atr_29086-33,C,T,TTGTCAACGGGTTT,TTGTCAATGGGTTT,GGTTTGGTTCAACCGCACAG,0,0
   3 Atr_29414-61,C,T,TTCCAACCGGGGAT,TTCCAACTGGGGAT,CAGGGCTGGGGTCTGGA,0,0
   3 Atr_39071-73,G,A,CTTCACAGAC,CTTCACAAAA,ATAGCCCAGGTGGATGCATG,0,0
   3 Atr_4677-47,C,G,TCCCGGACCGGGCC,TCCCGGAGCGGGCC,CCTGACACTGGCACTCAACA,0,0
   3 Atr_48754-60,G,A,CTGCAACGACGTGT,CTGCAACAACGTGT,GCTTTCTCCTTTCAGTGGCC,0,0
   3 Atr_525-66,G,C,AACAAGAAGCAAAGA,AACAACAAGCAAAGA,TCCAGCATGACCATCTCTGC,0,0
   3 Atr_61171-66,C,T,GATGTGACTGCACG,GATGTGATTGCACG,CCGACGCTGTAAGTTCTGGA,0,0
   3 Atr_69217-58,A,G,TCAAAGCACCCGAG,TCAAAGCGCCCGAG,AAGCCCCCTTTCTGCTTCTC,0,0
   3 Atr_7793-68,C,A,CGGTACTCAAATAA,CGGTACTAAAATAA,TAGGGAAAGGGAGTCAGCCA,0,0
   3 Atr_9723-56,C,T,ATGCGCAGTCTGTAG,ATGCGTAGTCTGTAG,TGATGGGCCATCTTTCACGG,0,0
   4 Atr_44473-38,T,C,ACATTGATATCTCA,ACATTGACATCTCA,GCAGGTGGTGGAGCTCATAG,0,2
   4 Atr_49388-52,G,A,CATGTGTGTCTGTC,CATGTGTATCTGTC,GGGACCCATGTATAAGATGGCC,0,0
   4 Atr_5019-45,C,T,TCCTGCAGC[TA]TTCCT,TCCTGTAGC[TA]TTCCT,GCACCGCTGAATGCTACATC,0,0.3
   4 Atr_51999-44,A,G,AATATAATGGGTAAG,AATATGATGGGTAAG,TAGGGTCCCAGGGCAGTTTA,0,0
   4 Atr_54160-70,T,C,TCATTTTTGGGTC,TCATTTTCGGGTC,TTTGCGGTTCAGATGTGGGT,0,0
   4 Atr_59842-43,G,A,GGCGGTTGAACCAG,GGCGGTTAAACCAG,CATCTCTCTTGTGAGGGCGG,0,1.2
   4 Atr_64006-52,C,T,GGTTTACCCTGAAG,GGTTTACTCTGAAG,CTGGATGGGGAGCGGTTTAC,0,0
   4 Atr_64706-45,T,A,CACTGACTGCTGTA,CACTGACAGCTGTA,TGCAGGGATGGTCCTTGTTG,1.9,0
   4 Atr_70167-40,C,T,CAGACCTCGTCCTG,CAGACCTTGTCCTG,GCATGCATCAGATAGCCAGC,0,0
   4 Atr_70479-48,T,A,CATAGATTGCTTCA,CATAGATAGCTTCA,GTCTGGGAAATGTCTGGGCA,1.8,0
   5 Atr_13917-71,C,A,AACTACTCATCA,AACTACTAATCA,CCTTCCCAGGGAGCTTGATG,0,0
   5 Atr_24146-56,A,C,ACATGTTAATCTTG,ACATGTTCATCTTG,TGGCTAAAGATCTAGAACACATGT,0,0
   5 Atr_28411-65,A,G,GTGCCCAACAGGAC,GTGCCCAGCAGGAC,AAACCAAGCAGCGTCTGGAA,0,0
   5 Atr_29277-35,C,G,TGAAACAGCAGTATG,TGAAAGAGCAGTATG,GGATCGCTCTCTGCTTGTGA,0,0
   5 Atr_45890-59,G,T,GTGAGGAGACCTGT,GTGAGGATACCTGT,TAAGGGCTGCAGTGGTGAAG,1.6,0
   7 Atr_16803-66,C,T,GGCAGCACGCCTCT,GGCAGCATGCCTCT,CATGTTGTGTGTCCGGTGC,0,0
   7 Atr_57542-29,A,T,CCAGAAAATGGCTC,CCAGAAATTGGCTC,CTGGCCTTTGTCCTCCAGAA,0,0
   9 Atr_40110-57,G,A,TAGGGCCGCATGCA,TAGGGCCACATGCA,GCACTGTGCCACTGACATAT,0,0
   
Wow, so what happened with these guys?

```{sh, eval=FALSE}
gunzip -c ../200/snps-90-broodstock.geno.gz  | cut -f 1,2 > sites.txt
```

```{r}
polys<-read_tsv("outputs/203/sites.txt", col_names = c("Locus","Site")) %>% group_by(Locus) %>%
  mutate(SNPS=n())
polys  %>% select(Locus, SNPS) %>% unique() %>% arrange(-SNPS)
```


```{r}
pl<-polys  %>% select(Locus, SNPS) %>% unique() %>% arrange(-SNPS) %>% filter(SNPS>=4) %>% separate(Locus, sep=",", into = c("Loci","G1","G2","R1","R2","Primer","X1","X2"))
pl
```


Get genos

```{r}
load("outputs/201/reads.rda")
```

```{r}
combo<-reads %>% left_join(parents %>% select(Sample, Type), by=c("Sample"="Sample")) 
combo %>% select(Sample, Type) %>% unique() %>% group_by(Type) %>% summarize(Count=n())
```

```{r}
combo %>% filter(Locus %in% pl$Loci) %>% group_by(Locus, Genotype, Call) %>% summarize(Count=n())
```

```{r}
combo %>% filter(Locus %in% pl$Loci) %>% group_by(Locus, Genotype, Call) %>% summarize(Count=n()) %>%
  filter(Call=="A2HOM") %>% arrange(-Count)
```

```{r}
combo %>% filter(Locus %in% pl$Loci) %>% group_by(Locus, Genotype, Call) %>% summarize(Count=n()) %>% filter(Locus=="Atr_54160-70")
```

    
_1_  
   4 Atr_70479-48,T,A,CATAGATTGCTTCA,CATAGATAGCTTCA,GTCTGGGAAATGTCTGGGCA,1.8,0
   
(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCTGGGAAATGTCTGGGCA test.fastq --color | grep CATAGATTGCTTCA | wc
   3317    3317  338334
(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCTGGGAAATGTCTGGGCA test.fastq --color | grep CATAGATAGCTTCA | wc
     46      46    4692


Has a lot of missing data, other sites a lot more variable: not to self compute MAFs from vcf.
Could try something like this:
Atr_70479-52,G,A,TGGTCAGATGCCT,TGGTCAAATGCCT,GTCTGGGAAATGTCTGGGCA,1.8,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCTGGGAAATGTCTGGGCA test.fastq  --color | grep TGGTCAGATGCCT | wc
   1417    1417  144534
(base) maccamp@farm:~/kootenai/outputs/201$ grep GTCTGGGAAATGTCTGGGCA test.fastq  --color | grep TGGTCAAATGCCT | wc
   1959    1959  199818

_2_    4 Atr_70167-40,C,T,CAGACCTCGTCCTG,CAGACCTTGTCCTG,GCATGCATCAGATAGCCAGC,0,0

Mostly NA and A2 HOMS, 12/19 look nicely variable, looks like this is off target amplification. Sigh. not worth messing with. This leads to low counts.
(base) maccamp@farm:~/kootenai/outputs/201$ cat test.fastq | grep GCATGCATCAGATAGCCA --color  | grep CAGACCTCGTCCTG | wc
     86      86    8772
(base) maccamp@farm:~/kootenai/outputs/201$ cat test.fastq | grep GCATGCATCAGATAGCCA --color  | grep CAGACCTTGTCCTG | wc
    190     190   19380

Could do something like this:
Atr_00001-40,G,C,AGCCAGCAGCAC,AGCCACCAGCAC,GCATGCATCAGATAGCCAGC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ cat test.fastq | grep GCATGCATCAGATAGCCA --color   | grep AGCCAGCAGCAC | wc
   1915    1915  195330
(base) maccamp@farm:~/kootenai/outputs/201$ cat test.fastq | grep GCATGCATCAGATAGCCA --color   | grep AGCCACCAGCAC | wc
    119     119   12138

_3_    4 Atr_64706-45,T,A,CACTGACTGCTGTA,CACTGACAGCTGTA,TGCAGGGATGGTCCTTGTTG,1.9,0 (this one should work great, skipping)


_4_ Atr_28411-65 looks to be mostly A1 Hom
   5 Atr_28411-65,A,G,GTGCCCAACAGGAC,GTGCCCAGCAGGAC,AAACCAAGCAGCGTCTGGAA,0,0
   
(base) maccamp@farm:~/kootenai/outputs/201$ grep AAACCAAGCAGCGTCTGGAA test.fastq  --color | grep GTGCCCAACAGGAC | wc
   1538    1538  156876
(base) maccamp@farm:~/kootenai/outputs/201$ grep AAACCAAGCAGCGTCTGGAA test.fastq  --color | grep GTGCCCAGCAGGAC | wc
      7       7     714

There are definitely some variable sites screwing with this one, moving to site 58
Atr_28411-65,T,C,ATGAGTTCCTG,ATGAGTCCCTG,AAACCAAGCAGCGTCTGGAA,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep AAACCAAGCAGCGTCTGGAA test.fastq  --color | grep ATGAGTTCCTG | wc
   1544    1544  157488
(base) maccamp@farm:~/kootenai/outputs/201$ grep AAACCAAGCAGCGTCTGGAA test.fastq  --color | grep ATGAGTCCCTG | wc
   1683    1683  171666
   
_5_
Atr_13917-71

   5 Atr_13917-71,C,A,AACTACTCATCA,AACTACTAATCA,CCTTCCCAGGGAGCTTGATG,0,0

Need to adjust for mutation here in regex,
                 
Atr_13917-47,G,C,TTTTGTCTGAA,TTTTCTCTGAA,CCTTCCCAGGGAGCTTGATG,0,0

_6_    4 Atr_59842-43,G,A,GGCGGTTGAACCAG,GGCGGTTAAACCAG,CATCTCTCTTGTGAGGGCGG,0,1.2

(base) maccamp@farm:~/kootenai/outputs/201$ grep CATCTCTCTTGTGAGGGCGG test.fastq | grep GGCGGTTGAACCAG | wc
   1172    1172  119544
(base) maccamp@farm:~/kootenai/outputs/201$ grep CATCTCTCTTGTGAGGGCGG test.fastq | grep GGCGGTTAAACCAG | wc
    798     798   81396
    

This site (23) should work well , NA may be low copy number.

_6_ Atr_64706
                      CACTGACAGCTGTA
   4 Atr_64706-45,T,A,CACTGACTGCTGTA,CACTGACAGCTGTA,TGCAGGGATGGTCCTTGTTG,1.9,0
This site should work well , NA may be low copy number.

_7_ Atr_44473-38	
   4 Atr_44473-38,T,C,ACATTGATATCTCA,ACATTGACATCTCA,GCAGGTGGTGGAGCTCATAG,0,2
(base) maccamp@farm:~/kootenai/outputs/201$ grep GCAGGTGGTGGAGCTCATAG test.fastq | grep ACATTGATATCTCA | wc
   1208    1208  123216
(base) maccamp@farm:~/kootenai/outputs/201$ grep GCAGGTGGTGGAGCTCATAG test.fastq | grep ACATTGACATCTCA | wc
   1190    1190  121380

Should work well.

_8_    5 Atr_45890-59,G,T,GTGAGGAGACCTGT,GTGAGGATACCTGT,TAAGGGCTGCAGTGGTGAAG,1.6,0
Don't expect GT polymorphism her, is CA, also AG poly in binding site
(base) maccamp@farm:~/kootenai/outputs/201$ grep TAAGGGCTGCAGTGGTGAAG test.fastq  --color | grep GTGAGGAGACCTGT | wc
   1547    1547  157794
(base) maccamp@farm:~/kootenai/outputs/201$ grep TAAGGGCTGCAGTGGTGAAG test.fastq  --color | grep GTGAGGATACCTGT | wc
      0       0       0
(

Atr_45890-42,A,C,GAGGAGACCTGTCT,GAGGAGCCCTGTCT,TAAGGGCTGCAGTGGTGAAG,1.6,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep TAAGGGCTGCAGTGGTGAAG test.fastq  --color | grep GAGGAGACCTGTCT | wc
   1544    1544  157488
(base) maccamp@farm:~/kootenai/outputs/201$ grep TAAGGGCTGCAGTGGTGAAG test.fastq  --color | grep GAGGAGCCCTGTCT | wc
    872     872   88944

_9_    4 Atr_64006-52,C,T,GGTTTACCCTGAAG,GGTTTACTCTGAAG,CTGGATGGGGAGCGGTTTAC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color CTGGATGGGGAGC test.fastq  | grep GGTTTACCCTGAAG | wc
   1480    1480  150960
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color CTGGATGGGGAGC test.fastq  | grep GGTTTACTCTGAAG | wc
      5       5     510

Site 14 looks to be a better one to redesign on, GA

Atr_64006-14,G,A,AGCGGTTTACA,AGCAGTTTACA,CTGGATGGGGAGCGGTTTAC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color CTGGATGGGGAGC test.fastq  | grep  AGCGGTTTACA | wc
   4413    4413  450126
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color CTGGATGGGGAGC test.fastq  | grep  AGCAGTTTACA | wc
    157     157   16014

_10_    4 Atr_49388-52,G,A,CATGTGTGTCTGTC,CATGTGTATCTGTC,GGGACCCATGTATAAGATGGCC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGGACCCATGTATAAGATGGCC test.fastq  | grep CATGTGTGTCTGTC | wc -l
1282
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGGACCCATGTATAAGATGGCC test.fastq  | grep CATGTGTATCTGTC | wc -l
516

Trying site 47
Atr_49388-47,T,G,ATACCGTGTGAAC,ATACCGGGTGAAC,GGGACCCATGTATAAGATGGCC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGGACCCATGTATAAGATGGCC test.fastq  | grep ATACCGTGTGAAC | wc
   1797    1797  183294
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGGACCCATGTATAAGATGGCC test.fastq  | grep ATACCGGGTGAAC | wc
    638     638   65076
    
_11_ Atr_51999-44,A,G,AATATAATGGGTAAG,AATATGATGGGTAAG,TAGGGTCCCAGGGCAGTTTA,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color TAGGGTCCCAGGGCAGTTTA test.fastq | grep AATATAATGGGTAAG | wc
    494     494   50388
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color TAGGGTCCCAGGGCAGTTTA test.fastq | grep AATATGATGGGTAAG | wc
     73      73    7446

Looks to be TA polymorphic    sites 34/35 both poly
Atr_51999-34,A,G,GAATATAATGGGTA,GAATATGATGGGTAA,TAGGGTCCCAGGGCAGTTTA,0,0, no real improvement here

_12_     5 Atr_29277-35,C,G,TGAAACAGCAGTATG,TGAAAGAGCAGTATG,GGATCGCTCTCTGCTTGTGA,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGATCGCTCTCTGCTTGTGA test.fastq  | grep TGAAACAGCAGTATG | wc
    404     404   41208
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGATCGCTCTCTGCTTGTGA test.fastq  | grep TGAAAGAGCAGTATG | wc
   1084    1084  110568

This regex looks to hit a variable site, adjusting
Atr_29277-31,C,G,ATGAAACAGCAGT,ATGAAAGAGCAGT,GGATCGCTCTCTGCTTGTGA,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGATCGCTCTCTGCTTGTGA test.fastq  | grep ATGAAACAGCAGT | wc
    406     406   41412
(base) maccamp@farm:~/kootenai/outputs/201$ grep --color GGATCGCTCTCTGCTTGTGA test.fastq  | grep ATGAAAGAGCAGT | wc
   2544    2544  259488
   
_13_    7 Atr_57542-29,A,T,CCAGAAAATGGCTC,CCAGAAATTGGCTC,CTGGCCTTTGTCCTCCAGAA,0,0
(base) maccamp@farm:~/kootenai/outputs/201$ grep CTGGCCTTTGTCCTCCAGAA test.fastq | grep CCAGAAATTGGCTC | wc
   1695    1695  172890

(base) maccamp@farm:~/kootenai/outputs/201$ grep CTGGCCTTTGTCCTCCAGAA test.fastq | grep CCAGAAAATGGCTC | wc
    116     116   11832
Let's see if a linked SNP is ruining everything. Yes indeedy!

(base) maccamp@farm:~/kootenai/outputs/201$ grep CTGGCCTTTGTCCTCCAGAA test.fastq | grep CCAGAAATTGG | wc
   1709    1709  174318
   
(base) maccamp@farm:~/kootenai/outputs/201$ grep CTGGCCTTTGTCCTCCAGAA test.fastq | grep CCAGAATTTGG | wc
   1109    1109  113118

Atr_57542-29,A,T,CCAGAAATTGG,CCAGAATTTGG,GGATCGCTCTCTGCTTGTGA,0,0

_14_    5 Atr_24146-56,A,C,ACATGTTAATCTTG,ACATGTTCATCTTG,TGGCTAAAGATCTAGAACACATGT,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep TGGCTAAAGATCTAGAACACATGT test.fastq | grep ACATGTTAATCTTG | wc
    239     239   24378
(base) maccamp@farm:~/kootenai/outputs/201$ grep TGGCTAAAGATCTAGAACACATGT test.fastq | grep ACATGTTCATCTTG | wc
   2303    2303  234906

Looks like site 26, with polys at 30 and 33, a variant linked to something 

TGGCTAAAGATCTAGAACACATGTTAATCTTGACTAATTAAGACAATACTTGGTTCCATTAAGCAACAGAGCTCGGTTGAAGATCGGAAGAGCACACGTCT
TGGCTAAAGATCTAGAACACATGTTAATCGTGGCTAATTAAGCCAATAATTGGTGCAATTAAGCAACAGAGCTCGGTTGAAGATCGGAAGAGCACACGTCT

(base) maccamp@farm:~/kootenai/outputs/201$ grep TGGCTAAAGATCTAGAACACATGT test.fastq | grep ACATGTTAATC | wc -l
425
(base) maccamp@farm:~/kootenai/outputs/201$ grep TGGCTAAAGATCTAGAACACATGT test.fastq | grep ACATGTTCATC | wc -l
2318

Atr_24146-26,A,C,ACATGTTAATC,ACATGTTCATC,TGGCTAAAGATCTAGAACACATGT,0,0
Atr_24146-56,A,C,ACATGTTAATCTTG,ACATGTTCATCTTG,TGGCTAAAGATCTAGAACACATGT,0,0

_15_    7 Atr_16803-66,C,T,GGCAGCACGCCTCT,GGCAGCATGCCTCT,CATGTTGTGTGTCCGGTGC,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep CATGTTGTGTGTCCGGTGC test.fastq  | grep GGCAGCACGCCTCT --color | wc
   1082    1082  110364
(base) maccamp@farm:~/kootenai/outputs/201$ grep CATGTTGTGTGTCCGGTGC test.fastq  | grep GGCAGCATGCCTCT --color | wc
    555     555   56610

GGCAGCAC[A|G]

GGCAGCACG
Also some indel poly, skipping!

_16_ Atr_54160-70,T,C,TCATTTTTGGGTC,TCATTTTCGGGTC,TTTGCGGTTCAGATGTGGGT,0,0

(base) maccamp@farm:~/kootenai/outputs/201$ grep TTTGCGGTTCAGATGTGGGT test.fastq | wc
  16851   16851 1718802
(base) maccamp@farm:~/kootenai/outputs/201$ grep TTTGCGGTTCAGATGTGGGT test.fastq | grep TCATTTTTGGGTC | wc
    887     887   90474
(base) maccamp@farm:~/kootenai/outputs/201$ grep TTTGCGGTTCAGATGTGGGT test.fastq | grep TCATTTTCGGGTC  | wc
    765     765   78030

Hmmm.... Some cross amplification, but should work ok.

_17_   4 Atr_5019-45,C,T,TCCTGCAGC[TA]TTCCT,TCCTGTAGC[TA]TTCCT,GCACCGCTGAATGCTACATC,0,0.3

Trying site 31 as an alternative
Atr_5019-31,A,G,TTTCAAATCCTG,TTTCAAGTCCTG,GCACCGCTGAATGCTACATC,0,0.3

(base) maccamp@farm:~/kootenai/outputs/201$ grep GCACCGCTGAATGCTACATC test.fastq | grep TTTCAAATCCTG  | wc
   1072    1072  109344
(base) maccamp@farm:~/kootenai/outputs/201$ grep GCACCGCTGAATGCTACATC test.fastq | grep TTTCAAGTCCTG | wc
    480     480   48960

