---
title: "205-metrics"
output: html_document
date: "2024-08-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

Can we generate metrics from *genos files?

outputs/203 has .original and .edited files, moving these to outputs 205
outputs/205/edited
cp ../../203/*edited .
for file in *.edited; do mv -- "$file" "${file%.edited}.genos"; done

ouputs/205/original
cp ../../203/*original .
for file in *.original; do mv -- "$file" "${file%.original}.genos"; done


Aviva notes:
Next, run the compiling script. Make sure to run it FROM the file with the .genos files in it

```{unix}
srun -t 0:30:00 -c 4 --mem 5G ../scripts/GTseq_GenoCompile_v3_Tetra.pl
```

Next, make your summary figures to visualize basic data quality.

```{unix}
srun -t 00:30:00 -c 4 --mem 10G python3 ../scripts/GTseq_SummaryFigures_v3_Tetra.py
```


So I:
~/kootenai/data-processing-files-aviva/GTseq_GenoCompile_v3_Tetra.pl > ../original.genos
mv original.genos ./original/
(base) maccamp@farm:~/kootenai/outputs/205/original$  ~/kootenai/data-processing-files-aviva/GTseq_SummaryFigures_v3_Tetra.py
type the path to directory containing .genos files for library *use single quotes*
Format= '/home/user/...'
/home/maccamp/kootenai/outputs/205/original/
type the library name *use single quotes*
original


 ~/kootenai/data-processing-files-aviva/GTseq_GenoCompile_v3_Tetra.pl > ../edited.genos
 mv edited.genos ./edited/
 
 ~/kootenai/data-processing-files-aviva/GTseq_SummaryFigures_v3_Tetra.py
/home/maccamp/kootenai/outputs/205/edited/
type the library name *use single quotes*
edited

From here you should be able to work with other programs like Polygene, Colony etc. using the ".genos" genotype files.


raceback (most recent call last):
  File "/home/maccamp/kootenai/data-processing-files-aviva/GTseq_SummaryFigures_v3_Tetra.py", line 211, in <module>
    otreads = int(OTarr[1])/1000
IndexError: list index out of range


Using broodstock org from outputs/201 locally in outputs/205/broodstock

for file in *.org; do mv -- "$file" "${file%.org}.genos"; done
expect 317 broodstock

Putting on farm, then
~/kootenai/data-processing-files-aviva/GTseq_GenoCompile_v3_Tetra.pl > ../broodstock.genos
mv broodstock.genos ./broodstock/

(base) maccamp@farm:~/kootenai/outputs/205/broodstock$ ~/kootenai/data-processing-files-aviva/GTseq_SummaryFigures_v3_Tetra.py
type the path to directory containing .genos files for library *use single quotes*
Format= '/home/user/...'
/home/maccamp/kootenai/outputs/205/broodstock/
type the library name *use single quotes*
broodstock 

this takes long enough I should probably cue it 

```{sh, eval=FALSE}
srun -t 00:30:00 -c 4 --mem 10G python3 ~/kootenai/data-processing-files-aviva/GTseq_SummaryFigures_v3_Tetra.py

```