---
title: "102.1-nas.Rmd"
output: html_document
date: "2023-10-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
setwd("~/github/kootenai/")
```

Several loci are invariant in terms of missing data. Let's see if they are actually polymorphic.

Atr_28746-28 appears to be invariant in the data set.
Atr_32545-55	appears to be invariant in the data set.
Atr_32551-51	appears to be invariant in the data set
Atr_63076-27	appears to be invariant in the data set


```{r,eval=FALSE}
save(ddf, file="/Users/mac/github/kootenai/outputs/102/ddf.rda")
```

```{r}
load("/Users/mac/github/kootenai/outputs/102/ddf.rda")
```
Any loci that are mostly one call?

```{r}
ddf %>% filter(Count > 1630*.6)
invariant<-ddf %>% filter(Count > 1630*.6)
```

```{r}
calls<-ddf %>% filter(Locus %in% invariant$Locus)
homs<-read_csv("~/github/kootenai/meta/invariant-loci.tsv", col_names = c("Locus"))
```

```{r}
calls %>% ungroup() %>% filter(Locus != homs$Locus)
```

Check to see if these are invariant:

Atr_10322-43 has more polymorphism @ site 56, already changed.

Atr_10428-71	I would expect to have more polymorphism.  Tow mostly polymorphic sites

Atr_10428-71,T,A,AGAGAGCTAGCA,AGAGAGCAAGCA,CGCACACACACAAAGAGAGC
             AGAGAGCTAGCA
CGCACACACACAAAGAGAGCTAGCAGCCCTGGCTTCCTGGAGTGTGGAGAGCTCACAGACACTGTGGCTCTGGATCCAGATCGGAAGAGCACACGTCTGAA
CGCACACACACAAAGAGAGCAAGCAGCCCTGGCTTTCTGGAGTGTGGAGAGCTAACAGACACTGTGGCTCTGGATCCAGATCGGAAGAGCACACGTCTGAA
             AGAGAGCAAGCA

Site 21 should be showing up with a bit of polymorphism (ame site)

Atr_10867 is invariant 

Some polymorphism here:
Atr_14862-38,T,C,TTGACTCCCTTTAAG,TTGACCCCCTTTAAG,CGCCTCCCCAGGACTATTTT,0,0
Atr_19666-61

